Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
add description of G4

>>>>

The fourth (and last) set of benchmarks considers the following description for the plant 
$G_{4}(s)$ extracted from Keel and Bhattacharyya~\cite{bhattacharyya97,keel_Bhattacharyya_examples}.
%
\begin{equation}
\label{exampleA}
G_{4}(s)=\frac{s-1}{s^{2}-s-2}
\end{equation}
%
\noindent where $G_{4}(z)$ is obtained using the ZOH discretisation defined 
in Eq.~\eqref{eq:pulsetf} with $3$ different sample times ($0.1$, $0.05$, and $0.03$ 
seconds); and the controllers are synthesised using $4$, $8$, and $12$-bits.
